\documentclass[11pt,article]{memoir}
% Copyright (C) 2013 Andrew Gainer-Dewar <andrew.gainer.dewar@gmail.com>
% This file may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either
% version 1.2 of this license or (at your option) any later
% version. The latest version of this license is in:
% http://www.latex-project.org/lppl.txt
% and version 1.2 or later is part of all distributions of
% LaTeX version 1999/12/01 or later.
\usepackage{agd-evaluation}

\coursenum{}
\coursename{}
\courseterm{}
\courseplace{Carleton College}
\courseinst{Dr.\ Andrew Gainer-Dewar}
\instructions{
  Please fill this evaluation out thoughtfully and honestly.
  Your responses will inform future teaching decisions, and no effort will be made to determine who wrote what.
}

\begin{document}
\maketitle

\begin{rankquestions}
  \rankquestion{The class sessions (lecture, discussions, etc.) were helpful in meeting my objectives in the course.}
  \rankquestion{The homework assignments were helpful in meeting my objectives in the course.}
  \rankquestion{The amount of time and effort required for this course was reasonable.}
  \rankquestion{The exams reflected the important concepts of the course.}
  \rankquestion{The course stimulated my interest in mathematics.}
  \rankquestion{I would recommend this course to a friend.}
  \rankquestion{The instructor was effective at fostering discussion in the classroom.}
  \rankquestion{The instructor was effective at helping me understand difficult topics.}
  \rankquestion{The instructor showed a genuine interest in my progress.}
  \rankquestion{The instructor was sufficiently available for office hours and appointments.}
  \rankquestion{The instructor was responsive to the needs of the students in the class.}
  \rankquestion{I would recommend this instructor to a friend.}
\end{rankquestions}

\begin{saquestions}
  \saquestion{What were the strengths of the instructor and the course?}
  \clearpage
  \saquestion[1.5in]{What do you wish you had known on the first day of class?}
  \saquestion[1.5in]{What was the one most important thing you learned in this course?}
  \saquestion[1.5in]{What concept from this course did you find to be the most difficult to understand?}
  \saquestion[1.5in]{What (excluding the instructor!) should be changed the next time this course is taught?}
  \saquestion{Do you have any other comments about the course or the instructor?}
\end{saquestions}
\end{document}
